Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-10 main.tex
minor changes in related work, addressed 2 of Henning's notes, added first picture to static experiments

    \subsection{Workflow}
    \label{sec.mod.work}
    A workflow is modeled as a directed acyclic graph $G=(V, E)$, where $V$ is the set of vertices (tasks), and
    $E$ is a set of directed edges of the form $e=(u,v)$, with $u,v\in V$, expressing precedence constraints between tasks.
    Each task~$u \in V$  is performing $w_u$ operations, and it also
    requires some amount of memory to be executed, denoted as~$m_u$.
    Each edge $e=(u,v) \in E$ has a cost~$c_{u,v}$ that corresponds to the size of the output file written by task~$u$ and used as input by task~$v$.
   Note that $m_u$ is the total memory usage
    of a task during its execution, including input and output files currently being read and written,
    and hence the total memory requirement  for the execution of task~$u$ consists of the maximum
    between the input files
    (total size of the files to be received from the parents),
    the output files (total size of the files to be sent to the children),
    and the total memory size~$m_u$ (usually achieving the maximum):
    \[
        r_u = \max\left\{m_u , \sum_{v:(v,u)\in E}c_{v,u}, \sum_{v:(u,v)\in E} c_{u,v}\right\}.
    \]
\AB{I transformed the sum into a max, correct? Or maybe we could assume $r_u=m_u$? }
\hmey{I  recall a discussion of the sum with Svetlana, but the text says max, it seems.}

@@

    \subsection{Early list schedulers with unlimited processors}
    An entire cluster of works on list schedulers has been carried out as early as the 90s.
    They all assume a DAG-shaped workflow with makespan weights on tasks, and an unlimited amount of homogeneous processors
    with the speed of 1.\hmey{needs refs or at least a survey pointer}

    The \textit{task duplication}-based approaches exploit that sometimes running a task twice on different machines can
    help reduce the makespan by saving communication costs.
    The two categories are scheduling with partial duplication~(SPD), and with full duplication~(SFD).
    For a join task (a task whose incoming degree is larger than its outgoing degree), SPD finds a critical immediate
    parent (the one that gives the largest start time to the join task) and duplicates only it.
    SFD duplicates all parents of a join node.
    Ref.~\cite{dfrn1997} proposes a task duplication algorithm. \hmey{The prev. sentence sounds odd since we are in the paragraph on task duplication.}
    It duplicates first (creates copies of all parent tasks) and then reduces (removes) the ones that can be removed without harming the makespan.
    The critical path fast duplication algorithm \texttt{CPFD}~\cite{5727760} classifies tasks into three categories: critical
    path task, in-branch task, or out-branch task.
    It schedules critical path tasks first, then in-branch tasks.
    \hmey{I'm missing the connection to our paper. Or vice versa, how is our contribution
    connected to these works? (Einordnung in den Forschungskontext) For example, do we do similar things? Are there interesting limitations we overcome?}

    Linear clustering~\cite{KWOK1999381} acts on critical paths in the workflow.
    It assigns the current critical path to one processor, removes all these tasks from the workflow, recomputes the critical
    path and repeats the procedure.
    \texttt{Heaviest node first}~\cite{SHIRAZI1990222} \hmey{Really typewriter for algorithms?
    Plus: this is not done consistently yet!} assigns the tasks level by level; 
    in each level, it schedules the one with largest computation time first.

@@

    PEFT (Predict earliest finish time)~\cite{arabnejad2014list} is a HEFT variant that computes an Optimistic
    Cost Table (OCT).
    The OCT is computed per task-processor pair and stores the longest shortest path from this task to the target task if this
    processor is chosen for this task.
    Ranking is based on OCT values.
    The processor choice stage minimizes the optimistic EFT, which is EFT plus the longest path to the exit node for each task.

@@

    The \texttt{SDC} algorithm~\cite{SHI2006665} considers the percentage of feasible processors in addition to task’s
    average execution cost in its weight.
    The selected task is then assigned to a processor which minimizes its Adjusted Earliest Finish Time (AEFT) that
    additionally notes how large the communication between current node and its children will be on the
    average provided that it is scheduled on the current processor.

@@

    \paragraph{Normal cluster}
    \skug{OLD DATA here, rewrite}

    Preliminary data: HEFT has 50\% failures, our algorithms have no failures.
    memory utilization blc is 5\% better, makespan 1\% worse.

>>>>

    \subsection{Workflow}
    \label{sec.mod.work}
    A workflow is modeled as a directed acyclic graph $G=(V, E)$, where $V$ is the set of vertices (tasks), and
    $E$ is a set of directed edges of the form $e=(u,v)$, with $u,v\in V$, expressing precedence constraints between tasks.
    Each task~$u \in V$  is performing $w_u$ operations, and it also
    requires some amount of memory to be executed, denoted as~$m_u$.
    Each edge $e=(u,v) \in E$ has a cost~$c_{u,v}$ that corresponds to the size of the output file written by task~$u$ and used as input by task~$v$.
   Note that $m_u$ is the total memory usage
    of a task during its execution, including input and output files currently being read and written,
    and hence the total memory requirement  for the execution of task~$u$ consists of the maximum
    between the input files
    (total size of the files to be received from the parents),
    the output files (total size of the files to be sent to the children),
    and the total memory size~$m_u$ (usually achieving the maximum):
    \[
        r_u = \max\left\{m_u , \sum_{v:(v,u)\in E}c_{v,u}, \sum_{v:(u,v)\in E} c_{u,v}\right\}.
    \]
    \AB{I transformed the sum into a max, correct? Or maybe we could assume $r_u=m_u$? }
    \hmey{I  recall a discussion of the sum with Svetlana, but the text says max, it seems.}
    \skug{it used to be  a sum, but not anymore since the collaboration with B1}

@@

    \subsection{Early list schedulers with unlimited processors}
    An entire cluster of works on list schedulers has been carried out as early as the 90s.
    They all assume a DAG-shaped workflow with makespan weights on tasks, and an unlimited amount of homogeneous processors
    with the speed of 1~\cite{benoit2013survey}.\hmey{needs refs or at least a survey pointer}
    \skug{actually, Anne cited them, so citing her :-)}

    The \textit{task duplication}-based approaches exploit that sometimes running a task twice on different machines can
    help reduce the makespan by saving communication costs.
    The two categories are scheduling with partial duplication~(SPD), and with full duplication~(SFD).
    For a join task (a task whose incoming degree is larger than its outgoing degree), SPD finds a critical immediate
    parent (the one that gives the largest start time to the join task) and duplicates only it.
    SFD duplicates all parents of a join node.
    The algorithm by~\cite{dfrn1997} duplicates first (creates copies of all parent tasks) and then reduces (removes) the ones that can be removed without harming the makespan.
    The critical path fast duplication algorithm CPFD~\cite{5727760} classifies tasks into three categories: critical
    path task, in-branch task, or out-branch task.
    It schedules critical path tasks first, then in-branch tasks.
    \hmey{I'm missing the connection to our paper. Or vice versa, how is our contribution
    connected to these works? (Einordnung in den Forschungskontext) For example, do we do similar things? Are there interesting limitations we overcome?}

    Linear clustering~\cite{KWOK1999381} acts on critical paths in the workflow.
    It assigns the current critical path to one processor, removes all these tasks from the workflow, recomputes the critical
    path and repeats the procedure.
    Heaviest node first~\cite{SHIRAZI1990222} assigns the tasks level by level;
    in each level, it schedules the one with largest computation time first.

@@

    PEFT (Predict earliest finish time) algorithm~\cite{arabnejad2014list} is a HEFT variant that computes an Optimistic
    Cost Table OCT.
    OCT is computed per task-processor pair and stores the longest shortest path from this task to the target task, if this
    processor is chosen for this task.
    Ranking is based on OCT values.
    Processor choice stage minimizes the Optimistic EFT, which is EFT plus the the longest path to the exit node for each task.

@@

    The SDC algorithm~\cite{SHI2006665} considers the percentage of feasible processors in addition to task’s
    average execution cost in its weight.
    The selected task is then assigned to a processor which minimizes its Adjusted Earliest Finish Time (AEFT) that
    additionally notes how large the communication between current node and its children will be on the
    average provided that it is scheduled on the current processor.

@@

    \paragraph{Normal cluster}

    On a normal cluster, the baseline \heft had $24.2\%$ success rate ($75.7\%$ failure rate).
    All the heuristics could schedule all workflows. \skug{check this tomorrow for two weird failures}.

    Figure~\ref{fig:ms-relations} shows the relations of the makespans foound by the heuristics to the makespans found by the baseline.
    On average, the makespans found by \heftbl are $7.8\%$ worse than those found by the baseline, the makespans of \heftblc are $8\%$
    worse, and those found by \heftmm are $71\%$ worse.

    \skug{TODO: how much worse are makespans for SUCCESSFUL hefts? presulmably almost identical}

    \begin{figure}[tb]
        \centering
        \includegraphics[width=0.495\columnwidth] {images/MsRelations}
        \caption{Relative makespans produced by the heuristics to the makespan produced by the baseline. Smaller is better.}
        \label{fig:ms-relations}
        \vspace{-0.3cm}
    \end{figure}
